A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-26 ms.tex
Update Bernardi et al 2014 to Bernardi et al 2015
from 572244e:
============

In eor.bib,

(*) Update Bernardi et al. 2014 to Bernardi et al. 2015

In ms.tex,

(*) Update Bernardi et al. 2014 to Bernardi et al. 2015

These uncertainties are presented only to confirm the qualitative agreement already seen between Figures~\ref{fig:fhd_data} and \ref{fig:sim_data}. These estimates are conservative. A full treatment of all uncertainties and deviations from ideal behavior such as frequency dependent errors in tile power pattern \citep{ber14}, calibration \citep{dat10}, data corruption due to interference, anisoplanatic wide--field imaging and ionospheric effects \citep{int09} will bring the simulations much closer in agreement with observations, but is beyond the scope of this paper. {\bf Hereafter}, our primary objective is to explore in detail the foreground signatures embedded in the {\it foreground wedge}.

>>>>

These uncertainties are presented only to confirm the qualitative agreement already seen between Figures~\ref{fig:fhd_data} and \ref{fig:sim_data}. These estimates are conservative. A full treatment of all uncertainties and deviations from ideal behavior such as frequency dependent errors in tile power pattern \citep{ber15}, calibration \citep{dat10}, data corruption due to interference, anisoplanatic wide--field imaging and ionospheric effects \citep{int09} will bring the simulations much closer in agreement with observations, but is beyond the scope of this paper. {\bf Hereafter}, our primary objective is to explore in detail the foreground signatures embedded in the {\it foreground wedge}.
